Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-08-14 man/tables/t_sampled_plots.Rmd
update

---
output:
  word_document:
    reference_docx: ../../templates/template_tables_portrait.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecosystems.csl
editor_options: 
  chunk_output_type: console
---

>>>>

---
output:
  word_document:
    reference_docx: ../../templates/template_tables_portrait.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecosystems.csl
---
